\clearpage
\pagebreak
{
	\centering
	\Huge Summary
	\par
}

\paragraph{}
\Large
Aravinth is an interdisciplinary expert with 17+ years of global experience in science, engineering, arts and sustainability, with the core expertise in research, development and production of electro-mechanical embedded systems and digital products.

As an engineer, he worked for 2 big corporates in the telecom sector and worked for 8 tech startups in the sector of education, smart home, media, agriculture, energy, healthcare \& water, in Asia \& Europe, where one of the hardware products was sold in 30K+ quantities and one of the software products reached 10M+ users.

As an entrepreneur, he co-founded 7 organisations in the sector of education, sustainability, agriculture, consulting \& engineering services, in Asia \& Europe.

As a scientist, he researched at 4 academic research institutions in the field of wireless technologies, autonomous vehicles, biometrics, humanoid robotics \& machine learning, in Germany.

As an educator, he trained several young innovators and mentored 120+ deep tech startups in the domain of advanced materials, healthcare, agriculture, aerospace, energy, automotive \& biotechnology, globally.

As an advisor, he is affiliated with 23 organisations and supported several individuals, startups, accelerators, incubators, innovation hubs, corporates, investors, manufacturers, research institutions, universities, government initiatives, art galleries and social enterprises, in more than 50 countries.

As an artist, he has co-created several new media art installations for temporary and permanent exhibitions, which attracted more than 1.5 million visitors, in Germany, Australia \& USA.

As a community builder, he co-created and has been curating several communities for startups, sustainability, education \& art, in Asia, Europe \& Africa.

\clearpage
