\section{Projects} 
List of freelancing projects for private clients, academic research projects, new media art projects, Hackathon challenge and personal projects.

\begin{longtable}
	{r|p{13cm}} 

	\textsc{2016} & \textbf{Swan Lake Music Art}, \emph{Private, Berlin, Germany}\\
	&\footnotesize{Swan Lake Music Art is a project of electronics and firmware to provide monotonic music for a multilayer painting about Russian Ballet which is painted by a fine artist who has been working on the project to exhibit the beauty of Ballet dance. Since the painting is on thinner canvas, the form factor of electronic should be thinner and smaller.}\\
	&\footnotesize{\textbf{Technology}: Tchaikovsky SwanLake Music, Attiny85, Monotone, AVR, Kicad, Arduino ISP, Piezo, Musescore, Midi, PWM, 440Hz}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/swan-lake-music-art}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2015} & \textbf{Gesture Recognition for Human-Robot Interaction: An approach based on skeletal points tracking using depth camera}, \emph{Master Thesis, Distributed Artificial Intelligence Lab, Berlin, Germany}\\
	&\footnotesize{Gesture Recognition For Human-Robot Interaction with modelling, training, analysing and recognising gestures based on computer vision and machine learning techniques.}\\
	&\footnotesize{\textbf{Technology}: HRI, Aldebaran NAO, Humanoid Robot, Depth Camera, AsusXtion, OpenNI2, NiTE2, Boost, UDP, WebSocket, ThreeJS, Matlab, C++, Javascript, Python, Gesture Recognition Toolkit, Adaptive Naive Bayes Classifier, Machine Learning, Robotics, 3D printing}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/gesture-recognition-for-human-robot-interaction}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2015} & \textbf{Heart of The City}, \emph{New Media Art Installation for VIVID Light Festival 2015, Sydney, Australia}\\
	&\footnotesize{The Heart of the City is an interactive public art sculpture that pulses light according to the heart beat of the people. The sculpture invites several people to sit and interactive with it.}\\
	&\footnotesize{\textbf{Technology}: Heartbeat sensing, Pulse Oximeter, Arduino, LED Neon Flex, Circuit Design, Power MOSFET STP16NF06L}\\
	\footnotesize{Link}&\footnotesize{\url{http://www.anaisafranco.com/heartofthecity}, \url{https://github.com/AravinthPanch/heart-of-the-city}}\\
	
	\multicolumn{2}{c}{} \\
		
	\textsc{2014} & \textbf{Smart Green House}, \emph{Research, Telecommunication Networks Group, TU Berlin, Germany}\\
	&\footnotesize{Smart Green House is a scalable plant monitoring system that helps us to monitor our plants and water them automatically.}\\
	&\footnotesize{\textbf{Technology}: IEEE.802.15.4, WaspMote, XBee, Light Sensor TSL2561, Moisture Sensor Temperature-Humidity Sensor DHT11, NodeJS}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/smart-green-house}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2013} & \textbf{RSSI based Indoor localization and Raw Ranging Data Visualization}, \emph{Research, Telecommunication Networks Group, TU Berlin, Germany}\\
	&\footnotesize{Indoor localisation using RSSI. RSSI is received signal strength indicator in IEEE 802.11 beacon packet and beacon packets are transmitted periodically to announce the presence of WiFi.}\\
	&\footnotesize{\textbf{Technology}: IEEE.802.11, Beacon Packet, RSSI, NodeJS, D3JS, Matlab, TWIST Testbed, Signal Jammer, WiSpy Spectrum Analyzer, Turtlebot, ROS, Javascript, Python}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/rssi}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2008} & \textbf{GSM Cell Phone controlled Two Axes Robot with artificial intelligence for the detection of Fire, Temperature and Metal}, \emph{Bachelor Thesis, SRM University, Chennai, India}\\
	&\footnotesize{The objective is to control a Robot over a long terrestrial distance by using GSM Network instead of using other communication technologies which have shorter range.}\\
	&\footnotesize{\textbf{Technology}: Two axis Robot, GSM cell phones with DTMF, DTMF receiver – UM92870, Sensors to detect temperature, fire and metal (IR LED, LDR, NTC), Micro Controller – 89c51, Buzzer}\\
		
	\multicolumn{2}{c}{} \\
		
	\textsc{2014} & \textbf{Stereo Acoustic Light Emitter}, \emph{Hackathon Challenge, Science Hackday Berlin 2014}, \textbf{Best Data Hack Award}\\
	&\footnotesize{It is an audio-visual system that makes use of spectral Tube and  sensors to create a feedback system.}\\
	&\footnotesize{\textbf{Technology}: spectral tube, OSC, MIDI synthesizer, Arduino, proximity sensor, infrared sensor, touch sensor, microphone, circuit board}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/stereo-acoustic-light-emitter}}\\
		
	\multicolumn{2}{c}{} \\
		
	\textsc{2014} & \textbf{Confusion}, \emph{New Media Art Installation, Creative Code Jam, Berlin, Germany}\\
	&\footnotesize{Confusion is an emotional sculpture in the form of a head with two faces that talks with the spectator when someone touches it.}\\
	&\footnotesize{\textbf{Technology}: Acrylic, Laser cutting, Plasma ball with Tesla coil, Current sensor, Arduino, MP3 shield, speakers}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/confusion-sensitive-sculpture}, \url{http://www.anaisafranco.com/confusion}}\\
	
	\multicolumn{2}{c}{} \\
		
	\textsc{2014} & \textbf{Home DNS}, \emph{Personal, Internet of Things}\\
	&\footnotesize{Home DNS is simple tool that will allow us to access our home LAN over internet. }\\
	&\footnotesize{\textbf{Technology}: NodeJS, RaspberryPi, Cloud, Port forwarding}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/home-dns}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2014} & \textbf{Yetu CAM}, \emph{Research, Yetu AG, Berlin, Germany}\\
	&\footnotesize{Yetu CAM is a simple telepresence robot. A telepresence robot is a remote-controlled, wheeled device with a display to enable video chat and videoconferencing, among other purposes.}\\
	&\footnotesize{\textbf{Technology}: Arduino Yun, 360 deg Servo Motor, MDF Laser Cut}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/yetu-cam}}\\
	
	\multicolumn{2}{c}{} \\
		
	\textsc{2013} & \textbf{StreeMuFi}, \emph{Hackathon Challenge, Hack4Good, Berlin, Germany}, \textbf{Winner}\\
	&\footnotesize{Street Music Finder (StreeMuFi) is a project to help street musicians earn a living with their music. Here you can search for street musicians and ask them to play a gig at your event.}\\
	&\footnotesize{\textbf{Technology}: PHP, Android, NodeJS, MySQL, GeekList}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/streemufi}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2013} & \textbf{Autonomous Vehicle}, \emph{Research, Daimler Center for Automotive Information Technology Innovations (DCAITI), Berlin, Germany }\\
	&\footnotesize{Vehicle-to-Vehicle Communication for autonomous vehicle to support Cooperative Adaptive Cruise Control (CACC) and Media Prefetching.}\\
	&\footnotesize{\textbf{Technology}: Java, VSimRTI Simulation, Mercedes Benz, v2v, v2x}\\

	\multicolumn{2}{c}{} \\
	
	\textsc{2014} & \textbf{Academics-LMU}, \emph{Freelance, Liaoning Medical University, Liaoning, China}\\
	&\footnotesize{E-Learning web application for medical students to attend various test series.}\\
	&\footnotesize{\textbf{Technology}: Wordpress, WPLMS, PHP, My SQL}\\
	\footnotesize{Link}&\footnotesize{\url{http://academics-lmu.com}}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2013} & \textbf{Shanti CRM}, \emph{Freelance, Bevermann Telesalesfactory, Berlin, Germany}\\
	&\footnotesize{Customized CRM based on Microsoft Dynamics CRM to manage marketing campagne.}\\
	&\footnotesize{\textbf{Technology}: Microsoft Dynamics CRM, SIP, Visual Studio, WPF, MVVM, Javascript}\\
	
	\multicolumn{2}{c}{} \\
	
	\textsc{2007} & \textbf{Steganography}, \emph{Freelance, SRM University, Chennai, India}\\
	&\footnotesize{Steganography is the art or practice of concealing a file, message, image, or video within another file, message, image, or video.}\\
	&\footnotesize{\textbf{Technology}: Visual Basic, Image Processing, RGB}\\
	\footnotesize{Link}&\footnotesize{\url{https://github.com/AravinthPanch/steganography}}\\
		
	\multicolumn{2}{c}{} \\
	
	\textsc{2003} & \textbf{Interactive Anatomy}, \emph{Freelance, Moscow Medical Academy, Moscow, Russia}\\
	&\footnotesize{Interactive application for medical students to learn anatomy of human body.}\\
	&\footnotesize{\textbf{Technology}: Flash, Sound Forge, Photoshop}\\
		

\end{longtable}